\section*{Depth-3 checks}

\paragraph{Goal.}
Check the lifted rank-pattern formulas explicitly when \(L=3\).

\paragraph{Lifted admissible intervals.}
For \(L=3\), the lifted admissible set is
\[
\widetilde{\mathcal I}_3^{\mathrm{wt}}
=
\{(0,0),(0,1),(0,2),(0,3),
(1,1),(1,2),(1,3),
(2,2),(2,3),(2,4),
(3,3),(3,4),(3,5)\}.
\]
The wrapped intervals are
\[
(2,4),\qquad (3,4),\qquad (3,5),
\]
corresponding respectively to
\[
2\to 3\to 0,\qquad 3\to 0,\qquad 3\to 0\to 1.
\]

\paragraph{Distinguished scalar coordinates.}
In these coordinates,
\[
\rho_{03}=\operatorname{rank}(W_3W_2W_1),
\qquad
\rho_{34}=\operatorname{rank}(W_0).
\]
Hence the fixed-arrow slice attached to a rank-\(r\) singular subset satisfies
\[
\rho_{34}=d_3-r,
\]
and its rank-\(r\) cyclic locus satisfies in addition
\[
\rho_{03}=r.
\]

\paragraph{Full-rank recovery.}
If \(r=d_3\), then
\[
\rho_{34}=0.
\]
Therefore every wrapped multiplicity vanishes:
\[
m_{24}=m_{34}=m_{35}=0.
\]
Only the ten chain intervals remain, namely
\[
(0,0),(0,1),(0,2),(0,3),(1,1),(1,2),(1,3),(2,2),(2,3),(3,3),
\]
which is exactly the equioriented type-\(A_4\) classification governing the
global-minimum fiber.

\paragraph{A useful sanity check.}
The unique length-\(3\) interval is \((0,3)\). Hence
\[
m_{03}=\rho_{03}.
\]
This matches the general statement that the open-chain rank is the multiplicity
of the unique maximal indecomposable and confirms that the rank-\(r\) condition
is encoded by one scalar rank-pattern coordinate.

\paragraph{Status.}
Completed. The depth-3 case matches the general formulas and recovers the
expected global-minimum picture when \(r=d_3\).
