\section*{Task 1: Forward formula}

\paragraph{Goal.}
Express the lifted rank pattern in terms of the indecomposable multiplicities.

\paragraph{Lifted multiplicity coordinates.}
Write a multiplicity pattern in lifted coordinates as
\[
m=(m_{uv})_{(u,v)\in \widetilde{\mathcal I}_L^{\mathrm{wt}}},
\]
where \(m_{uv}\) is the multiplicity of the indecomposable interval module
\[
M(u,v).
\]

\paragraph{Containment criterion on indecomposables.}
On a lifted interval module \(M(u,v)\), the path \(q_{ab}\) acts with rank
\[
1
\]
if and only if the path interval \([a,b]\) is contained in the support interval
\([u,v]\), and otherwise the rank is \(0\).

Indeed, \(M(u,v)\) is one-dimensional on every vertex of \([u,v]\), every arrow
inside \([u,v]\) acts as the identity, and every arrow outside \([u,v]\) acts
as \(0\). Therefore the composition along \(q_{ab}\) is the identity exactly in
the containment case.

\paragraph{Forward formula.}
For the module
\[
M\cong \bigoplus_{(u,v)\in \widetilde{\mathcal I}_L^{\mathrm{wt}}}
M(u,v)^{\oplus m_{uv}},
\]
one has, for every \((a,b)\in \widetilde{\mathcal I}_L^{\mathrm{wt}}\),
\[
\rho_{ab}(M)
=
\sum_{\substack{(u,v)\in \widetilde{\mathcal I}_L^{\mathrm{wt}}\\
u\le a\le b\le v}}
m_{uv}.
\]
This is just additivity of rank over direct sums together with the containment
criterion above.

\paragraph{Two important specializations.}
The open-chain path \([0,L]\) is contained only in the unique maximal interval
\([0,L]\). Hence
\[
\rho_{0L}(M)=m_{0L}.
\]
The closing arrow \([L,L+1]\) is contained exactly in the wrapped intervals, so
\[
\rho_{L,L+1}(M)
=
\sum_{\substack{(u,v)\in \widetilde{\mathcal I}_L^{\mathrm{wt}}\\
u\le L<L+1\le v}}
m_{uv}.
\]
This is the lifted form of the closing-arrow rank functional from the current
draft.

\paragraph{Status.}
Completed. The forward map from multiplicities to rank data is now explicit and
already singles out the two scalar coordinates relevant for the DLN slice.
