\section*{Task 4: Fixed-arrow compatibility}

\paragraph{Goal.}
Rewrite the fixed-arrow and rank-\(r\) conditions in lifted rank-pattern
coordinates.

\paragraph{Closing-arrow compatibility.}
Let \(W\in \Gamma_{d,S}\). By definition of the fixed-arrow slice,
\[
q_{L,L+1}(W)=W_0=\Sigma_{XY}P_Q.
\]
Hence
\[
\rho_{L,L+1}(W)=\operatorname{rank}(W_0).
\]
Under the standing assumption that \(\Sigma_{XY}\) has full rank \(d_L\) and
\(|S|=r\), this equals
\[
\operatorname{rank}(W_0)=d_L-r.
\]

\paragraph{Open-chain rank compatibility.}
If \(W\in \Gamma_{d,S}^r\), then
\[
q_{0L}(W)=W_L\cdots W_1=\mu(W),
\]
so
\[
\rho_{0L}(W)=\operatorname{rank}(\mu(W))=r.
\]

\paragraph{Rank-pattern formulation of the slice constraints.}
Define
\[
\widetilde{\mathcal R}_{d,S}^{\mathrm{real}}
:=
\{\rho(W)\mid W\in \Gamma_{d,S}\}
\subseteq
\widetilde{\mathcal R}_d^{\mathrm{wt}},
\]
and
\[
\widetilde{\mathcal R}_{d,S}^{\mathrm{real},r}
:=
\{\rho(W)\mid W\in \Gamma_{d,S}^r\}.
\]
Then the multiplicity classification from the second-conjecture block and the
bijection of Task 3 give
\[
\widetilde{\mathcal R}_{d,S}^{\mathrm{real}}
=
\{\rho\in \widetilde{\mathcal R}_d^{\mathrm{wt}}\mid \rho_{L,L+1}=d_L-r\},
\]
and
\[
\widetilde{\mathcal R}_{d,S}^{\mathrm{real},r}
=
\{\rho\in \widetilde{\mathcal R}_d^{\mathrm{wt}}\mid \rho_{L,L+1}=d_L-r,\ \rho_{0L}=r\}.
\]

\paragraph{Reason.}
The current draft already proves that realized multiplicity patterns are exactly
those for which the wrapped-interval count equals \(\operatorname{rank}(W_0)\).
By Task 1, that wrapped-interval count is precisely the lifted coordinate
\(\rho_{L,L+1}\). By the special case \(m_{0L}=\rho_{0L}\) from Task 2, the
rank-\(r\) condition is exactly the scalar constraint \(\rho_{0L}=r\).

\paragraph{Full-rank case.}
If \(r=d_L\), then
\[
\rho_{L,L+1}=0.
\]
Hence no wrapped interval is allowed, so the realized rank patterns reduce to
the ordinary type-\(A\) patterns on the chain
\[
0\to 1\to \cdots \to L.
\]
This is the direct weight-space recovery of the global-minimum regime.

\paragraph{Status.}
Completed. The fixed closing arrow and the end-to-end rank are now encoded by
the two scalar coordinates \(\rho_{L,L+1}\) and \(\rho_{0L}\).
