\section*{Task 5: Rank-pattern orbit stratification}

\paragraph{Goal.}
Rewrite the fixed-arrow orbit classification of the cyclic locus using the
lifted rank-pattern labels.

\paragraph{Rank-pattern strata.}
For
\[
\rho\in \widetilde{\mathcal R}_d^{\mathrm{wt}},
\]
define
\[
\Gamma_{d,S}[\rho]
:=
\{W\in \Gamma_{d,S}\mid \rho(W)=\rho\},
\qquad
\Gamma_{d,S}^r[\rho]
:=
\Gamma_{d,S}[\rho]\cap \Gamma_{d,S}^r.
\]

\paragraph{Orbit classification in rank-pattern coordinates.}
The assignment
\[
W\longmapsto \rho(W)
\]
induces a bijection
\[
G_d^{W_0}\backslash \Gamma_{d,S}
\xrightarrow{\sim}
\{\rho\in \widetilde{\mathcal R}_d^{\mathrm{wt}}\mid \rho_{L,L+1}=d_L-r\}.
\]
Equivalently,
\[
\Gamma_{d,S}
=
\bigsqcup_{\rho_{L,L+1}=d_L-r}\Gamma_{d,S}[\rho],
\]
and every nonempty piece \(\Gamma_{d,S}[\rho]\) is a single
\(G_d^{W_0}\)-orbit.

Restricting to the rank-\(r\) slice gives
\[
G_d^{W_0}\backslash \Gamma_{d,S}^r
\xrightarrow{\sim}
\{\rho\in \widetilde{\mathcal R}_d^{\mathrm{wt}}\mid \rho_{L,L+1}=d_L-r,\ \rho_{0L}=r\},
\]
equivalently
\[
\Gamma_{d,S}^r
=
\bigsqcup_{\substack{\rho\in \widetilde{\mathcal R}_d^{\mathrm{wt}}\\
\rho_{L,L+1}=d_L-r,\ \rho_{0L}=r}}
\Gamma_{d,S}^r[\rho],
\]
with each nonempty stratum a single \(G_d^{W_0}\)-orbit.

\paragraph{Proof.}
The second-conjecture theorem in the current draft classifies
\(G_d^{W_0}\)-orbits by realized multiplicity patterns. Task 3 identifies
multiplicity patterns with lifted rank patterns, and Task 4 identifies the
realized and rank-\(r\) realized subsets by the scalar constraints on
\(\rho_{L,L+1}\) and \(\rho_{0L}\). Composing these bijections yields the
result.

\paragraph{What this accomplishes.}
This is the direct weight-space version of the old residual-space orbit
stratification by cyclic rank patterns. The labels are now attached directly to
the fixed-arrow cyclic locus inside parameter space, without passing through the
residual formalism.

\paragraph{Status.}
Completed. Conjecture 3 is now proved at the cyclic-locus level in lifted
rank-pattern coordinates.
