\section*{Codimension checks}

\paragraph{Goal.}
Validate the codimension formulas against the main special cases.

\paragraph{Check 1: full-rank case.}
If \(r=d_L\), then
\[
W_0=0,
\qquad
\Gamma_{d,S}^{d_L}=\Sigma_d^{d_L}.
\]
The general relation gives
\[
\operatorname{codim}_{\Omega}\mathcal C_{d,S}^{d_L}
=
\operatorname{codim}_{\Omega}\Sigma_d^{d_L}+d_0d_L.
\]
Since the full-rank determinantal locus is open in \(\Omega\) under the
no-bottleneck assumption, one obtains
\[
\operatorname{codim}_{\Omega}\mathcal C_{d,S}^{d_L}=d_0d_L,
\]
which is exactly the expected codimension of the fiber
\(\mu^{-1}(P_SW^\ast)\).

\paragraph{Check 2: relation with the cyclic slice.}
For every \(r\),
\[
\operatorname{codim}_{\Omega}\mathcal C_{d,S}^r
-\operatorname{codim}_{\Omega}\Gamma_{d,S}^r
=
r(d_0-d_L+r).
\]
The right-hand side depends only on the reduced endpoint problem, not on the
internal orbit label. This matches the geometric picture from the orbit
correspondence: every cyclic orbit loses the same endpoint-orbit dimension when
it is intersected with the critical fiber.

\paragraph{Check 3: depth three.}
For \(L=3\), the codimension functional is evaluated on the same thirteen lifted
interval labels listed in the third- and fourth-conjecture checks. In the
full-rank case the three wrapped intervals disappear, and the formula reduces to
the standard chain-type computation.

\paragraph{Status.}
Completed. The codimension formulas pass the main sanity checks, including the
global-minimum benchmark.
